Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-17 krs-survey.tex
{Modifying->Alteration} of knowledge structures
Added ref to ACT-R/E

This exclude \textit{de facto} classical cognitive systems like {\sc Soar} or
{\sc ACT-R} for which we could not find recent implementations on full-scale
service robots.

@@

\subsubsection{Modifying the knowledge structure}

>>>>

While classical cognitive systems like {\sc Soar} or {\sc ACT-R} have
declarative knowledge modules and have been recently used on service robots
(see {\sc ACT-R/E}~\cite{Kennedy2009} for instance), they are absent from this
survey because we could not find evidence in the litterature on possible
on-line manipulation of symbolic knowledge.

@@

\subsubsection{Alteration of the knowledge structure}

In systems
